---
title: "R Notebook"
output: html_notebook
---

---
title: "ADHD Programmers Analysis -- Medication Split"
output: html_notebook
author: "A1"
date: "2024-07-16"
---

```{r}
source("standard_cleaning.R")
nrow(data)

# Drop Q73_5 -- it was not answered by anyone
data = subset(data, select = -Q73_5)

# Make task competency be numeric
data[116:122] = lapply(data[116:122], function(x) as.numeric(x))
```

# Change group to respect the analysis we're doing (checking if medication matters for any differences)
```{r}
# Now want four levels of group: ADHD_med, ADHD_notmed, NT, non-ADHD ND
# ifelse(test, yes, no) --> can be nested
names(data)[134]
# Index of 134 is where it shows if they're medicated or not -- of course, this is an imperfect test, since we didn't ask if they were medicated for ADHD specifically.
data$group = ifelse(data$HasADHD, ifelse(is.na(data$strats_2), "ADHD_notmed", "ADHD_med"), ifelse(data$OtherND, "ND non-ADHD", "NT"))
data$group = factor(data$group)
data$group

# There could be a confound between the medicated and the diagnosed group, because you usually need to be diagnosed to take stimulants. Could do a chi-squared test between diagnosed and non-diagnosed on medication strategy. 
uses_meds = ifelse(!is.na(data$strats_2), "Uses meds", "Doesn't use meds")
data$diagnosis_status = as.logical(data$diagnosis_status)
table = table(data$diagnosis_status, uses_meds) # TRUE means they were diagnosed
table
t = chisq.test(table)
t
t$stdres

# Yep, huge confound.

# Drop all nondiagnosed ADHD'ers from data, since there's a huge confound here between getting diagnosed and getting medicated
data = data[(data$diagnosis_status | !data$HasADHD), ]
data
# should be 493 - 127 = 366 rows. yay
```

# Change levels of group so we're comparing to NT people
```{r}
tmp = subset(data, data$group == "ADHD")
tmp2 = subset(data, data$group == "NT")

mean(as.numeric(tmp$distract_1), na.rm = T)
mean(as.numeric(tmp2$distract_1), na.rm = T)

levels(data$group)

data$group = relevel(data$group, ref = "NT")
levels(data$group)

tmp = subset(data, data$group == "ADHD")
tmp2 = subset(data, data$group == "NT")

mean(as.numeric(tmp$distract_1), na.rm = T)
mean(as.numeric(tmp2$distract_1), na.rm = T)
```
# Local definition of polr row function
```{r}
m = polr(distract_1 ~ group + yoe + pmh_avg, data = data, Hess = TRUE, na.action = na.omit)
summary(m)

add_polr_row = function(curr_data, df, i, task_competency) {
  colname = colnames(curr_data)[i]
  print(paste("THIS IS THE TEST: ", colname))
  curr_data[[i]] = ordered(curr_data[[i]])
  
  # Make formula into string using paste
  # Simplest model
  formula = ""
  if (is.null(task_competency)) {
    formula = paste(colname, "~ group + yoe + pmh_avg + wfh_status")
  }
  else {
    formula = paste(colname, "~ group + yoe + pmh_avg + wfh_status +", task_competency)
  }
  
  print(formula)
  
  m = polr(formula, data = data, Hess = TRUE, na.action = na.omit)
  
  # Check prop odds assumption
  br = brant(m)
  omnibus = br[1, 3]
  
  # Check to see if the polr model is appropriate and keep that as data in the dataframe
  brant_pass = omnibus > .05
  
  # Extract z-values from the summary
  summary_polr = summary(m)
  z_values = summary_polr$coefficients[, "t value"]
  
  # Calculate p-values
  p_values = 2 * pnorm(-abs(z_values))
  if (is.null(task_competency)) {
    p_values = p_values[1:7]
  }
  else {
    p_values = p_values[1:8]
  }
  
  print(confint(m))
  new.row = data.frame()
  
  # Extract coefficients
  coefficients = coef(m)
  
  # Calculate odds ratios for each coefficient -- basically an effect size for how much sway each predictor has on the response variable. Increase by 1, or from reference value, increases the likelihood of increasing the response
  # variable by one level by [odds ratio] times
  odds_ratios = exp(coefficients)
  
  if (is.null(task_competency)) {
    new.row = data.frame(challenge = colname,
                         can_use = brant_pass,
                         adhdmedp = p_values[1],
                         adhdnonmedp = p_values[2],
                         ndp = p_values[3],
                         yoep = p_values[4],
                         pmhp = p_values[5],
                         hybridp = p_values[6],
                         wfhp = p_values[7])
  }
  
  else {
  new.row = data.frame(challenge = colname,
                         can_use = brant_pass,
                         adhdmedp = p_values[1],
                         adhdnonmedp = p_values[2],
                         ndp = p_values[3],
                         yoep = p_values[4],
                         pmhp = p_values[5],
                         hybridp = p_values[6],
                         wfhp = p_values[7],
                        compp = p_values[8])
  }
  odds_ratio_df = as.data.frame(t(odds_ratios))
  if (is.null(task_competency)) {
    colnames(odds_ratio_df) = c("coef_adhdmed", "coef_adhdnonmed", "coef_nd", "coef_yoe", "coef_pmh", "coef_hybrid", "coef_wfh")
  }
  else {
    colnames(odds_ratio_df) = c("coef_adhdmed", "coef_adhdnonmed", "coef_nd", "coef_yoe", "coef_pmh", "coef_hybrid", "coef_wfh", "coef_comp")
  }
  new.row = cbind(new.row, odds_ratio_df)
  df = rbind(df, new.row)
  return(df)
}
```


# Challenge Modeling By Software Task
```{r}
# Factors to put in polr formula: competency at task, group, yoe, pmh, wfh_status

challenges_df = data.frame(challenge = character(),
                           can_use = logical(),
                           adhdmedp = numeric(),
                           adhdnonmedp = numeric(),
                           ndp = numeric(),
                           yoep = numeric(),
                           pmhp = numeric(),
                           hybridp = numeric(),
                           wfhp = numeric(),
                           compp = numeric(),
                           coef_adhdmed = numeric(),
                           coef_adhdnonmed = numeric(),
                           coef_nd = numeric(),
                           coef_yoe = numeric(),
                           coef_pmh = numeric(),
                           coef_hybrid = numeric(),
                           coef_wfh = numeric(),
                           coef_comp = numeric())

comp_i = 116 # This is the index of best.tasks._1, or perceived competency at code review.

for (i in 53:59) {
  # Add task competency as a predictor to the formula by passing it into the function
  task_competency = colnames(data)[comp_i]
  challenges_df = add_polr_row(data, challenges_df, i, task_competency)
  comp_i = comp_i + 1
}

comp_i = 116

for (i in 64:70) {
  task_competency = colnames(data)[comp_i]
  challenges_df = add_polr_row(data, challenges_df, i, task_competency)
  comp_i = comp_i + 1
}

# Skip an index for best.tasks._4 -- 119 -- because that is meetings, which we don't ask about when it comes to "having trouble starting or continuing tasks" because it didn't make sense.

comp_i = 116

for (i in 72:77) {
  task_competency = colnames(data)[comp_i]
  challenges_df = add_polr_row(data, challenges_df, i, task_competency)
  if (comp_i == 118) {
    comp_i = comp_i +2
    next
  }
  comp_i = comp_i + 1
}

comp_i = 116

for (i in 78:91) {
  task_competency = colnames(data)[comp_i]
  challenges_df = add_polr_row(data, challenges_df, i, task_competency)
  if (comp_i == 122) {
    comp_i = 116
    next
  }
  comp_i = comp_i + 1
}

challenges_df

# Make a dataframe that's just the p values, then unlist and do BH correction and cat onto og dataframe
p_val_challenges = challenges_df[3:10]
p_val_challenges

# Combine all p-values into a single vector
all_pvalues = unlist(p_val_challenges)

# Apply BH correction to the combined p-values
all_pvalues_corrected = p.adjust(all_pvalues, method = "BH")

# Reshape the corrected p-values back into the original dataframe
df_corrected = as.data.frame(matrix(all_pvalues_corrected, nrow = nrow(p_val_challenges), byrow = FALSE))
colnames(df_corrected) = c("adhdmedp_adjusted", "adhdnonmedp_adjusted", "ndp_adjusted", "yoep_adjusted", "pmhp_adjusted", "hybridp_adjusted", "wfhp_adjusted", "compp_adjusted")

challenges_df = cbind(challenges_df, df_corrected)
challenges_df # Now has adjusted p_values side by side

```

# Look at the differences in significant challenges between the medication groups
```{r}
sig1 = which(challenges_df$adhdmedp_adjusted < .05)
sig2 = which(challenges_df$adhdnonmedp_adjusted < .05)
sig1 = challenges_df$challenge[sig1]
sig1
sig2 = challenges_df$challenge[sig2]
sig2

# These are the list of challenges that were significant in the original Rmd
# "distract_1" "distract_3" "distract_4" "distract_5" "distract_6" "distract_7" "Q55_1"      "Q55_2"      "Q55_3"      "Q55_4"      "Q55_5"      "Q55_6"      "Q55_7"      "Q73_2"      "Q73_3"      "Q73_4"     
# "Q73_7"      "Q73_8"      "Q53_1"      "Q53_2"      "Q53_3"      "Q53_4"      "Q53_5"      "Q53_6"      "Q53_7"      "Q60_1"      "Q60_3"      "Q60_4"      "Q60_5"      "Q60_6"      "Q60_7"

# These are the ADHD med group
# "distract_1" "distract_3" "distract_4" "distract_5" "distract_6" "distract_7" "Q55_1"      "Q55_2"      "Q55_3"      "Q55_4"      "Q55_5"      "Q55_6"      "Q55_7"      "Q73_2"      "Q73_4"      "Q73_6"     
# "Q73_7"      "Q73_8"      "Q53_1"      "Q53_2"      "Q53_3"      "Q53_4"      "Q53_5"      "Q53_6"      "Q53_7"      "Q60_1"      "Q60_2"      "Q60_3"      "Q60_4"      "Q60_5"      "Q60_6"      "Q60_7"

# "Q73_6" and "Q60_2" newly significant in medicated group
```


# Other Broad Challenge Questions
```{r}
# Go through last few challenges questions. Q56 and 57 are context switching and communication. 58 is ease of development environment. 89 is preferred interview types (chi square test). 91 is standup effects. 92 is pair programming effects. 94 is waiting for things, 95 is version control ease (git ease). 

challenges_broad_df = data.frame(challenge = character(),
                           can_use = logical(),
                           adhdmedp = numeric(),
                           adhdnonmedp = numeric(),
                           ndp = numeric(),
                           yoep = numeric(),
                           pmhp = numeric(),
                           hybridp = numeric(),
                           wfhp = numeric(),
                           compp = numeric(),
                           coef_adhddiag = numeric(),
                           coef_adhdnondiag = numeric(),
                           coef_nd = numeric(),
                           coef_yoe = numeric(),
                           coef_pmh = numeric(),
                           coef_hybrid = numeric(),
                           coef_wfh = numeric())

which(colnames(data) == "context_switching")
which(colnames(data) == "Q58")
which(colnames(data) == "Q91_1")
which(colnames(data) == "Q92_1")
which(colnames(data) == "wait_compile")

# Context switching
challenges_broad_df = add_polr_row(data, challenges_broad_df, 92, NULL)
# Communication
challenges_broad_df = add_polr_row(data, challenges_broad_df, 93, NULL)
# 
# # Ease of development environment
# challenges_broad_df = add_polr_row(data, challenges_broad_df, 95, NULL)

# The above won't work, I think due to colinearity or not enough per group

# Effects of standup on productivity, quality, and wellbeing
for (i in 103:105) {
  challenges_broad_df = add_polr_row(data, challenges_broad_df, i, NULL)
}

# Effects of pair programming on productivity, quality, and wellbeing
for (i in 107:109) {
  challenges_broad_df = add_polr_row(data, challenges_broad_df, i, NULL)
}

# Waiting for things to compile
challenges_broad_df = add_polr_row(data, challenges_broad_df, 110, NULL)
# Ease with version control
challenges_broad_df = add_polr_row(data, challenges_broad_df, 111, NULL)

# Make a dataframe that's just the p values, then unlist and do BH correction and cat onto og dataframe
p_val_challenges = challenges_broad_df[3:9]
p_val_challenges

# Combine all p-values into a single vector
all_pvalues = unlist(p_val_challenges)

# Apply BH correction to the combined p-values
all_pvalues_corrected = p.adjust(all_pvalues, method = "BH")

# Reshape the corrected p-values back into the original dataframe
df_corrected = as.data.frame(matrix(all_pvalues_corrected, nrow = nrow(p_val_challenges), byrow = FALSE))
colnames(df_corrected) = c("adhdmedp_adjusted", "adhdnonmedp_adjusted", "ndp_adjusted", "yoep_adjusted", "pmhp_adjusted", "hybridp_adjusted", "wfhp_adjusted")

challenges_broad_df = cbind(challenges_broad_df, df_corrected)
challenges_broad_df # Now has adjusted p_values side by side

```
# Broad challenges significance differences
```{r}
sig1 = which(challenges_broad_df$adhdmedp_adjusted < .05)
sig2 = which(challenges_broad_df$adhdnonmedp_adjusted < .05)
sig1 = challenges_broad_df$challenge[sig1]
sig1
sig2 = challenges_broad_df$challenge[sig2]
sig2

# In main notebook, "context_switching" "Q57" were significant
# none significant for non-medicated diagnosed ADHD devs

nrow(subset(data, group == "ADHD_notmed"))
# 35 is a small number of people to be doing this with, but not too bad for this kind of model
```

# Strength Modeling
```{r}
# Factors that could reasonably affect strengths: yoe, group, pmh (self efficacy)
strengths_df = data.frame(strat.name = character(),
                           can_use = logical(),
                           adhdmedp = numeric(),
                           adhdnonmedp = numeric(),
                           ndp = numeric(),
                           yoep = numeric(),
                           pmhp = numeric(),
                           coef_adhddiag = numeric(),
                           coef_adhdnondiag = numeric(),
                           coef_nd = numeric(),
                           coef_yoe = numeric(),
                           coef_pmh = numeric())

names(data[126])

for (i in 116:126) {
  colname = colnames(data)[i]
  print(paste("THIS IS THE TEST: ", colname))
  data[[i]] = ordered(data[[i]])
  levels(data[[i]])
  # Make formula into string using paste
  # Simplest model
  formula = paste(colname, "~ group + yoe + pmh_avg")
  m = polr(formula, data = data, Hess = TRUE, na.action = na.omit)
  
  # Extract coefficients
  coefficients = coef(m)
  
  # Calculate odds ratios for each coefficient -- basically an effect size for how much sway each predictor has on the response variable. Increase by 1, or from reference value, indicates the likelihood of increasing the response
  # variable by one level by [odds ratio] times (> 1 value means more likely to be higher, < 1 equals more likely to be lower on the scale)
  odds_ratios = exp(coefficients)
  odds_ratio_df = as.data.frame(t(odds_ratios))
  colnames(odds_ratio_df) = c("coef_adhdmed", "coef_adhdnonmed", "coef_nd", "coef_yoe", "coef_pmh")
  
  # Check prop odds assumption
  br = brant(m)
  summary(br)
  
  omnibus = br[1, 3]
  
  # Check to see if the polr model is appropriate and keep that as data in the dataframe
  brant_pass = omnibus > .05

  # Extract z-values from the summary
  summary_polr = summary(m)
  z_values = summary_polr$coefficients[, "t value"]

  # Calculate p-values
  p_values = 2 * pnorm(-abs(z_values))
  p_values = p_values[1:5]
  print(p_values)
  print(confint(m))
  new.row = data.frame(strat.name = colname,
                       can_use = brant_pass,
                       adhdmedp = p_values[1],
                       adhdnonmedp = p_values[2],
                       ndp = p_values[3],
                       yoep = p_values[4],
                       pmhp = p_values[5])
  new.row = cbind(new.row, odds_ratio_df)
  strengths_df = rbind(strengths_df, new.row)
}
# Make a dataframe that's just the p values, then unlist and do BH correction and cat onto og dataframe
p_val_strengths = strengths_df[3:7]
# p_val_strengths

# Combine all p-values into a single vector
all_pvalues = unlist(p_val_strengths)

# Apply BH correction to the combined p-values
all_pvalues_corrected = p.adjust(all_pvalues, method = "BH")

# Reshape the corrected p-values back into the original dataframe
df_corrected = as.data.frame(matrix(all_pvalues_corrected, nrow = nrow(p_val_challenges), byrow = FALSE))
print("MEOW")
colnames(df_corrected) = c("adhdmedp_adjusted", "adhdnonmedp_adjusted", "ndp_adjusted", "yoep_adjusted", "pmhp_adjusted")
# df_corrected

# strengths_df = cbind(strengths_df, df_corrected)
# strengths_df # Now has adjusted p_values side by side
```
# Strength significance differences
```{r}
sig1 = which(strengths_df$adhddiagp_adjusted < .05)
sig2 = which(strengths_df$adhdnondiagp_adjusted < .05)
sig1 = strengths_df$strat.name[sig1]
sig1
sig2 = strengths_df$strat.name[sig2]
sig2

# In the main analysis, "best.tasks._2" "best.tasks._6" "Q62"           "Q63"           "Q64"           "hyperfocus" were significant
# Interestingly, debugging proficiency goes away with ADHD diag group and stays with non-diag group, but brainstorming only present in the diag group (might want to look at autistic split for this before we publish)
```

